---
title: "Data Import"
output: github_document
---

```{r, echo = FALSE}
library(tidyverse)
library(readxl)
library(haven)
```

# Data Import: CSVs

Let's import data using the `readr` package. We want to use relative paths (meaning starting from the R project) to indicate where existing files are. We can also send this relative path to others with similar folder names, and they will be able to use it as well. 
```{r}
litters_df = read.csv("data_import_examples/FAS_litters.csv")
litters_df = janitor::clean_names(litters_df)
```

The `janitor` package exists on my computer. We are saying in the `janitor` package, use the `clean_names` function. `Janitor` has a bunch of other functions that we don't need. 

Next, let us look at the data 
```{r}
litters_df

head(litters_df)
tail(litters_df)
```

```{r, eval = FALSE}
view(litters_df)
```

```{r}
skimr::skim(litters_df)
```

We can explore `read_csv` options by inputting `?read_csv` in the console below. 
We are able to change set values to N/A in the dataset, depending on how they're set in the existing data set.You can also skip the first few lines of the dataset, since if say, there's irrelevant information.  

# Other File Formats

We need to read in an Excel spreadsheet. We used to need to export to CVS, re-import, etc. We can now we can just use the `readxl` package. Make sure you uplaod the package first (see above). Side note: ignore the LotR backup excel spreadsheet when committing - it will disappear after you close the file. 
```{r}
read_xlsx("data_import_examples/mlb11.xlsx")
```

# Still more formats...

Read in a SAS dataset. Load in `Haven` library first!
```{r}
pulse_df = read_sas("data_import_examples/public_pulse_data.sas7bdat")
```

# Data Export
Suppose you read in this LotR dataframe, and you want to save it somewhere (intermediate dataset, for example).The code is supposed to be `write_csv(lotr_words_df, file = "results/lotr_words_df.csv")` but it's not working for some reason. 

# GitIgnore
You can use gitignore to ignore a directory or file before you commit and push. You should also commit and push the actual gitignore file. This is useful for when you absolutely do not want to upload a dataset to git, e.g. if a dataset has patient data, or if it's simply too big. 


