---
title: "Data Import"
output: github_document
---

```{r, echo = FALSE}
library(tidyverse)
```

# Data Import: CSVs

Let's import data using the `readr` package. We want to use relative paths (meaning starting from the R project) to indicate where existing files are. We can also send this relative path to others with similar folder names, and they will be able to use it as well. 
```{r}
litters_df = read.csv("data_import_examples/FAS_litters.csv")
litters_df = janitor::clean_names(litters_df)
```

The `janitor` package exists on my computer. We are saying in the `janitor` package, use the `clean_names` function. `Janitor` has a bunch of other functions that we don't need. 

Next, let us look at the data 
```{r}
litters_df

head(litters_df)
tail(litters_df)
```

```{r, eval = FALSE}
view(litters_df)
```

```{r}
skimr::skim(litters_df)
```

We can explore `read_csv` options by inputting `?read_csv` in the console below. 
We are able to change set values to N/A in the dataset, depending on how they're set in the existing data set.You can also skip the first few lines of the dataset, since if say, there's irrelevant information.  
```{r}
read_csv( na = c("", "NA"))
read_csv(skip = 0)
```

# Other File Formats


